---
name: Chase M Clark
address: "University of Wisconsin-Madison, School of Pharmacy"
www: chasemc.github.io
email: "chasingmicrobes@gmail.com"
twitter: ChasingMicrobes
github: chasemc
linkedin: hirechase
date: "`r format(Sys.time(), '%B %Y')`"
output: function(...) {source('resume_entries.R');vitae:::set_entry_formats(resume_entries);vitae::cv_document(..., template = "resume_template.tex", citation_package = "biblatex")}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(data.table)
library(glue)
library(lubridate)
library(dplyr)
library(jsonlite)
library(rorcid)
orcid_auth()
pipe_assign <- function(x) x
```


```{r orcid-data}
rorcid::orcid_educations("0000-0001-6439-9397")$`0000-0001-6439-9397`$`affiliation-group`$summaries |>
  data.table::rbindlist(fill = T) |>
  pipe_assign() -> orcid_data
```

# Education

```{r employment}
temp <- cbind.data.frame(orcid_data[, c('education-summary.role-title','education-summary.end-date.year.value',
                                        'education-summary.organization.name')], 
                         paste0(orcid_data$'education-summary.organization.address.city',
                                ", ",
                                orcid_data$'education-summary.organization.address.region' ))

colnames(temp) <- c('Degree',
                    'Year',
                    'Institution',
                    'Where')

detailed_entries(data = temp,
                 what = Degree, 
                 when = Year,
                 with =  Institution,
                 where = Where)
```

# Employment

```{r experience}
job_titles <- data.table::fread(here::here("data", "job-titles.csv"), sep = "\t")

job_descriptions <- data.table::fread(here::here("data", "job-descriptions.csv"), sep = ",")

jobs <- merge(job_titles, 
                          job_descriptions, 
                          by = "jobId", 
                          all.x = T) 

data.table::setorderv(jobs,
                      c("begin","descId"),
                      order=c(-1, 1))


vitae::detailed_entries(jobs,
                        what = position,
                        when = as.character(
                          glue("{lubridate::month(begin, label = TRUE, abbr = TRUE)} {lubridate::year(begin)} - 
           {ifelse(!is.na(end), 
           paste(lubridate::month(end, label = TRUE, abbr = TRUE), lubridate::year(end)), 'present')}")),
           with = employer,
           where = glue("{city}, {region}, {country}"),
           why = accomplishments)
```

\newpage
<!-- 
# Skills

```{r, skills, results='asis', width = 40000}

skills <- data.table::fread(here::here("data", "skills.csv"))

skills_formatted <- skills %>% 
  mutate(skill = if_else(is.na(details), glue("{skill}"), glue("{skill} ({details})"))) %>% 
  group_by(group) %>% 
  summarize(skills = glue_collapse(skill, sep = " $\\bullet$ "))

skills_formatted$skills <- gsub("()", "",skills_formatted$skills,fixed = TRUE)

for (group in skills_formatted$group) {
  cat(
    glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"),
    filter(skills_formatted, group == !!group)$skills,
    "\n\n\n"
  )
}
```
-->

# Funding/Awards

```{r awards}

grants <- data.table::fread(here::here("data/awards.csv"), sep = "\t", fill=T)

grants$end <- ifelse(is.na(grants$end), "present", grants$end)
grants$year <- ifelse(is.na(grants$begin), grants$end, paste0(grants$begin, "-", grants$end))


brief_entries(data =  grants[order(grants$end, decreasing = T),],
              what = award,
              when = year,
              with = amount)

```

# Publications

```{r publications, include=FALSE}

puburls <- data.table::fread(here::here("data","papers.csv"))$doi
crossref_api <- paste0("https://api.crossref.org/v1/works/", puburls)

pubs <- lapply(crossref_api, 
               function(x){
                 jsonlite::fromJSON(x)$message
               })

pub_dates <- sapply(pubs, 
                    function(x){
                      paste0(x$published$`date-parts`[1:2], collapse = "/")
                    })

pub_dates <- as.Date(pub_dates, format = "%Y/%M")

keys <- order(pub_dates, decreasing = T)

publications_bibtex <- lapply(seq_along(pubs), 
                              function(x){
                                utils::toBibtex(
                                  utils::bibentry(
                                    bibtype = "Article",
                                    title = pubs[[x]]$title,
                                    author = paste0(paste0(pubs[[x]]$author$given, " ", pubs[[x]]$author$family), collapse = ", "),
                                    journal = paste0( pubs[[x]]$`container-title`, ". Citations: ", pubs[[x]]$`is-referenced-by-count`),
                                    year = pubs[[x]]$issued$`date-parts`[[1]],
                                    url = pubs[[x]]$DOI,
                                    note = paste0("Citations: ", pubs[[x]]$`is-referenced-by-count`),
                                    key=paste0(keys[[x]]))
                                )
                              })

publications_bibtex <- publications_bibtex[keys]

bibfilepath="pubs.bib"

if (file.exists(bibfilepath)){
  file.remove(bibfilepath)
}

con = file(description = bibfilepath, open = "a", blocking = TRUE,
           encoding = "UTF-8", raw = FALSE)

for (i in publications_bibtex){
  writeLines(i,con)
}

close(con)

```

```{r bibliography}
bibliography_entries(bibfilepath)
```

# Submitted Publications


- "Artificial Intelligence Approaches to Natural Product Drug Discovery" (Submitted to Nature Reviews Drug Discovery)
  - Michael W. Mullowney, Katherine R. Duncan, Somayah S. Elsayed, Neha Garg, Justin J.J. van der Hooft, Nathaniel I. Martin, David Meijer, Barbara Terlouw, Friederike Biermann, Kai Blin, Janani Durairaj, Marina Gorostiola González, Eric J.N. Helfrich, Florian Huber, Stefan Leopold-Messer, Kohulan Rajan, Tristan de Rond, Jeffrey A. van Santen, Maria Sorokina, Marcy J. Balunas, Mehdi A. Beniddir, Doris van Bergeijk, Laura M. Carroll, **Chase M. Clark**, Chris Dejong, Chao Du, Scarlet Ferrinho, Francesca Grisoni, Albert Hofstetter, Willem Jespers, Olga V. Kalinina, Satria A. Kautsar, Tiago F. Leao, Joleen Masschelein, Evan R. Rees, Raphael Reher, Daniel Reker, Philippe Schwaller, Marwin Segler, Michael A. Skinnider, Allison S. Walker, Egon Willighagen, Barbara Zdrazil, Nadine Ziemert, Rebecca J.M. Goss, Pierre Guyomard, Andrea Volkamer, William H. Gerwick, Hyun Uk Kim, Rolf Müller, Gilles P. van Wezel, Gerard van Westen, Anna K.H. Hirsch, Roger Linington, Serina L. Robinson, Marnix H. Medema



# Talks

```{r talks}

oral <- data.table::fread(here::here("data/oral_contributed.csv"), sep = "\t")

detailed_entries(data = oral[order(as.Date(oral$year), decreasing = T),],
                 what = meeting, 
                 when = as.character(glue("{lubridate::month(year, label = TRUE, abbr = TRUE)} {lubridate::year(year)} ")),
                 why = title)
```


# In-Progress

```{r ongoing}

ongoing <- data.table::fread(here::here("data/ongoing_projects.csv"), sep = "\t", fill=T)

detailed_entries(data = ongoing,
                 what = description,
                 when = name)
#                 why = status)

```

# Select Individual Software Projects

```{r software-individual}

software <- data.table::fread(here::here("data/software.csv"), sep = "\t")

software <- software[software$group == "solo", ]

detailed_entries(data = software[order(software$year, decreasing = T),],
                 what = name,
                 when = year,
                 with = language,
                 where = description)
```

# Select Team Software Projects

```{r software-team}

software <- data.table::fread(here::here("data/software.csv"), sep = "\t")

software <- software[software$group == "team", ]

detailed_entries(data = software[order(software$year, decreasing = T),], 
                 what = name,
                 when = year,
                 with = language,
                 where = description)

```


# Workshops (host)

```{r workshops1}
#workshops <- data.table::fread(here::here("data/workshops_led.csv"), sep = "\t")
#
#setorderv(workshops,
#          c("begin"),
#          order=-1)
#
#detailed_entries(workshops,
#                 what = name,
#                 when = as.character(
#                   glue("{lubridate::month(begin, label = TRUE, abbr = TRUE)} {lubridate::year(begin)} "))
#)

workshops <- data.table::fread(here::here("data/workshops_led.csv"), sep = "\t")

detailed_entries(data = workshops[order(as.Date(workshops$year), decreasing = T),],
                 what = meeting, 
                 when = as.character(glue("{lubridate::month(year, label = TRUE, abbr = TRUE)} {lubridate::year(year)} ")),
                 why = title)
```
\newpage

# Workshops (participant)
```{r workshops}
workshops <- data.table::fread(here::here("data/workshops_participant.csv"), sep = "\t")

setorderv(workshops,
          c("begin"),
          order=-1)

detailed_entries(workshops,
                 what = name,
                 when = as.character(glue("{lubridate::month(begin, label = TRUE, abbr = TRUE)} {lubridate::year(begin)} "))
)
```



# Teaching

## Invited Guest Lectures

```{r teaching-invited}
# year	university	course
invited_guest_lecture <- data.table::fread(here::here("data/invited_guest_lecture.tsv"), sep = "\t")

detailed_entries(data = invited_guest_lecture[order((invited_guest_lecture$year), decreasing = T),],
                 what = course, 
                 when = year,
                 where = university)
```

# Peer Review

- Journal of Natural Products

- CRC press

- rOpenSci

- Microbiology Spectrum

# Memberships/Professional Affiliations

- American Society of Pharmacognosy
- Chicago R User Group
- Chicago Python User group

---

The code for building this CV is available at:
https://github.com/chasemc/resume
