%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Chase M Clark}{}

\address{University of Wisconsin-Madison, School of Pharmacy}

\email{\href{mailto:chasingmicrobes@gmail.com}{\nolinkurl{chasingmicrobes@gmail.com}}}
\homepage{chasemc.github.io}
\github{chasemc}
\linkedin{hirechase}
\twitter{ChasingMicrobes}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {October 2023}
    {Chase M Clark~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{PhD Pharmacognosy}{University of Illinois Chicago}{Chicago, IL}{2015}{}\vspace{-4.0mm}
    \cventry{BS Biochemistry}{Berry College}{Mount Berry, GA}{2008}{}\vspace{-4.0mm}
    \cventry{Principia Consortium Study Abroad}{University of Glasgow}{Glasgow, Glasgow}{2010}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{employment}{%
\section{Employment}\label{employment}}

\begin{cventries}
    \cventry{Computation and Informatics in Biology and Medicine (CIBM) Postdoctoral Fellow}{}{Remote, Chicago, IL}{Jun 2021 - 
present}{\begin{cvitems}
\item Appointment to UW-Madison/National Library of Medicine T15 training grant
\item Developing genomic and metagenomic bioinformatics software
\item Currently developing a repository-scale analysis platform for comparative genomics
\end{cvitems}}
    \cventry{Postdoctoral Research Associate}{University of Wisconsin-Madison}{Remote, Chicago, IL}{Sep 2020 - 
present}{}\vspace{-4.0mm}
    \cventry{NIH F31 Fellow}{University of Illinois at Chicago}{Chicago, IL, US}{May 2019 - 
Aug 2020}{}\vspace{-4.0mm}
    \cventry{Ph.D. Student}{University of Illinois at Chicago}{Chicago, IL, US}{Aug 2015 - 
Aug 2020}{\begin{cvitems}
\item Natural product drug dicovery, specifically bacterial-derived antibiotics
\item Conceived, learned to code, and built a bioinformatics program (R Shiny app) for rapid bacterial metabolomics analyses
\item Isolated and cultured 1000’s of bacterial isolates and performed natural product isolation and structure elucidation
\item First or co-first author on four studies/manuscripts
\item Mentored undergradaute and graduate students leading to publishable studies
\end{cvitems}}
    \cventry{Research and Development Technician}{Deerland Probiotics \& Enzymes}{Kennesaw, GA, US}{Mar 2013 - 
Aug 2015}{\begin{cvitems}
\item Assisted in the design and results analysis of three clinical studies
\item Presented monthly projects to CEO, VP Sales and VP Science \& Technology
\item Head of method development and identification of raw materials to meet CFR 21, FDA requirements.
\item Developed identifications for over 140 materials, from enzymes and botanicals to minerals and additives. 
\item Overhauled the Method Development Department establishing inter-departmental responsibilities, improving and creating new SOPs, streamlining identification requests by establishing a formal request  process and interactive database
\item Strengthened and created new relationships with third-party vendors, labs, and universities. 
\item Controlled budget of method development for purchase of standards, consumables, equipment and third-party testing.
\item Mentored interns from Kennesaw Mountain High School magnet program
\end{cvitems}}
    \cventry{Bonner Scholar}{Bonner Foundation}{Rome, GA, US}{Aug 2008 - 
May 2012}{\begin{cvitems}
\item Four-year community service scholarship requiring weekly and summer commitments.
\end{cvitems}}
\end{cventries}

\newpage

\hypertarget{select-fundingawards}{%
\section{Select Funding/Awards}\label{select-fundingawards}}

\begin{cvhonors}
    \cvhonor{}{Computation and Informatics in Biology and Medicine (CIBM) Training Program (T32)}{~\$100,000.00}{2021-present}
    \cvhonor{}{St. Jude National Graduate Student Symposium (cancelled due to Covid19)}{One of ~40 participants selected from ~1,000 invite-only applications}{2020}
    \cvhonor{}{NIH Predoctoral Individual National Research Service Award (F31)}{~\$90,000.00}{2019-2020}
    \cvhonor{}{R/Pharma, Travel Award}{\$500}{2018}
    \cvhonor{}{W.E. van Doren Scholar}{\$1,000}{2017}
    \cvhonor{}{American Society of Pharmacognosy Student Travel Award}{\$600}{2017}
    \cvhonor{}{University of Illinois at Chicago Provost/Deiss Award}{\$2,500}{2017}
    \cvhonor{}{Bonner Scholar}{Scholarship for students with financial need ``in exchange for weekly commitment to intensive and meaningful service with a local community organization over the four years''}{2008-2012}
    \cvhonor{}{Academic Scholarship}{}{2008-2012}
    \cvhonor{}{McCaleb, Hubert Scholarship}{}{2011}
    \cvhonor{}{Frank Plummer Scholarship}{}{2011}
    \cvhonor{}{Griggs Academic Scholarship}{}{2010}
    \cvhonor{}{John R. Bertrand Scholarship}{}{2009}
    \cvhonor{}{Sierra Club College Scholarship}{}{2008}
    \cvhonor{}{Cherokee Area Eagle Scout of the Year Scholarship}{}{2008}
\end{cvhonors}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-6000}{}}%
Mullowney, M. W., \ldots, \textbf{Clark, C. M.}.C.M., \ldots, \& Medema,
M. H. (2023). Artificial intelligence for natural product drug
discovery. \emph{Nature Reviews Drug Discovery. Citations: 0}.
\href{https://10.1038/s41573-023-00774-7}{10.1038/s41573-023-00774-7}

\leavevmode\vadjust pre{\hypertarget{ref-6}{}}%
Rees, E. R., Uppal, S., \textbf{Clark, C. M.}.C.M., Lail, A. J.,
Waterworth, S. C., Roesemann, S. D., Wolf, K. A., \& Kwan, J. C. (2023).
Autometa 2: A versatile tool for recovering genomes from highly-complex
metagenomic communities\emph{. Citations: 0}.
\href{https://10.1101/2023.09.01.555939}{10.1101/2023.09.01.555939}

\leavevmode\vadjust pre{\hypertarget{ref-7000}{}}%
Waterworth, S. C., Rees, E. R., \textbf{Clark, C. M.}.C.M., Carlson, S.,
Miller, I. J., Puglisi, M., \& Kwan, J. C. (2023). Elevated expression
of srp RiPPs across bacterial phyla in marine sponges\emph{. Citations:
0}. \href{https://10.1101/2023.06.09.544420}{10.1101/2023.06.09.544420}

\leavevmode\vadjust pre{\hypertarget{ref-10}{}}%
\textbf{Clark, C. M.}.C.M., Hernandez, A., Mullowney, M. W.,
Fitz-Henley, J., Li, E., Romanowski, S. B., Pronzato, R., Manconi, R.,
Sanchez, L. M., \& Murphy, B. T. (2022). Relationship between bacterial
phylotype and specialized metabolite production in the culturable
microbiome of two freshwater sponges. \emph{ISME Communications.
Citations: 2}.
\href{https://10.1038/s43705-022-00105-8}{10.1038/s43705-022-00105-8}

\leavevmode\vadjust pre{\hypertarget{ref-4}{}}%
\textbf{Clark, C. M.}.C.M., Nguyen, L., Pham, V. C., Sanchez, L. M., \&
Murphy, B. T. (2022). Automated microbial library generation using the
bioinformatics platform IDBac. \emph{Molecules. Citations: 2}.
\href{https://10.3390/molecules27072038}{10.3390/molecules27072038}

\leavevmode\vadjust pre{\hypertarget{ref-5}{}}%
Elfeki, M., Mantri, S., \textbf{Clark, C. M.}.C.M., Green, S. J.,
Ziemert, N., \& Murphy, B. T. (2021). Evaluating the distribution of
bacterial natural product biosynthetic genes across lake huron sediment.
\emph{ACS Chemical Biology. Citations: 4}.
\href{https://10.1021/acschembio.1c00653}{10.1021/acschembio.1c00653}

\leavevmode\vadjust pre{\hypertarget{ref-3}{}}%
Leao, T. F., \textbf{Clark, C. M.}.C.M., Bauermeister, A., Elijah, E.
O., Gentry, E. C., Husband, M., Oliveira, M. F., Bandeira, N., Wang, M.,
\& Dorrestein, P. C. (2021). Quick-start infrastructure for untargeted
metabolomics analysis in GNPS. \emph{Nature Metabolism. Citations: 8}.
\href{https://10.1038/s42255-021-00429-0}{10.1038/s42255-021-00429-0}

\leavevmode\vadjust pre{\hypertarget{ref-1}{}}%
\textbf{Clark, C. M.}.C.M., Murphy, B. T., \& Sanchez, L. M. (2020). A
call to action: The need for standardization in developing open-source
mass spectrometry-based methods for microbial subspecies discrimination.
\emph{mSystems. Citations: 2}.
\href{https://10.1128/msystems.00813-19}{10.1128/msystems.00813-19}

\leavevmode\vadjust pre{\hypertarget{ref-7}{}}%
Braesel, J., \textbf{Clark, C. M.}.C.M., Kunstman, K. J., Green, S. J.,
Maienschein-Cline, M., Murphy, B. T., \& Eustáquio, A. S. (2019). Genome
sequence of marine-derived streptomyces sp. Strain F001, a producer of
akashin a and diazaquinomycins. \emph{Microbiology Resource
Announcements. Citations: 2}.
\href{https://10.1128/mra.00165-19}{10.1128/mra.00165-19}

\leavevmode\vadjust pre{\hypertarget{ref-8}{}}%
\textbf{Clark, C. M.}.C.M., Costa, M. S., Conley, E., Li, E., Sanchez,
L. M., \& Murphy, B. T. (2019). Using the open-source MALDI TOF-MS IDBac
pipeline for analysis of microbial protein and specialized metabolite
data. \emph{Journal of Visualized Experiments. Citations: 9}.
\href{https://10.3791/59219}{10.3791/59219}

\leavevmode\vadjust pre{\hypertarget{ref-9}{}}%
Costa, M. S., \textbf{Clark, C. M.}.C.M., Ómarsdóttir, S., Sanchez, L.
M., \& Murphy, B. T. (2019). Minimizing taxonomic and natural product
redundancy in microbial libraries using MALDI-TOF MS and the
bioinformatics pipeline IDBac. \emph{Journal of Natural Products.
Citations: 16}.
\href{https://10.1021/acs.jnatprod.9b00168}{10.1021/acs.jnatprod.9b00168}

\leavevmode\vadjust pre{\hypertarget{ref-2}{}}%
\textbf{Clark, C. M.}.C.M., Costa, M. S., Sanchez, L. M., \& Murphy, B.
T. (2018). Coupling MALDI-TOF mass spectrometry protein and specialized
metabolite analyses to rapidly discriminate bacterial function.
\emph{Proceedings of the National Academy of Sciences. Citations: 66}.
\href{https://10.1073/pnas.1801247115}{10.1073/pnas.1801247115}

\hypertarget{talks}{%
\section{Talks}\label{talks}}

\begin{cventries}
    \cventry{How to write reproducible code for data science}{}{}{Sep 2023 }{\begin{cvitems}
\item Chicago R User Group
\end{cvitems}}
    \cventry{Reproducibly building and analyzing knowledge graphs for drug discovery with Nextflow, Neo4j and Python}{}{}{Aug 2023 }{\begin{cvitems}
\item Chicago Python User Group
\end{cvitems}}
    \cventry{SocialGene: Large Scale Knowledge Graphs for Microbial Based Drug Discovery}{}{}{Mar 2023 }{\begin{cvitems}
\item Computation and Informatics in Biology and Medicine Seminars
\end{cvitems}}
    \cventry{Information-Rich Platforms for Natural Product Antibiotic Drug Discovery and Microbial Characterization}{}{}{Jan 2023 }{\begin{cvitems}
\item Northeastern University Department of Chemistry and Chemical Biology
\end{cvitems}}
    \cventry{SocialGene: A Large Scale Search Engine to Find Metagenomic BGCs in Free-Living Organisms}{}{}{Jan 2023 }{\begin{cvitems}
\item 2023 ASP Younger Members Symposium
\end{cvitems}}
    \cventry{Large Scale Analysis of Protein Homology for Microbial Drug Discovery}{}{}{Jun 2022 }{\begin{cvitems}
\item National Library of Medicine (NLM) T15 Training Conference
\end{cvitems}}
    \cventry{Towards near-instant, repository-scale searching for homologous BGCs with Socialgene (Selected alternate speaker, didn't present)}{}{}{Mar 2022 }{\begin{cvitems}
\item Gordon Research Conference on Marine Natural Products
\end{cvitems}}
    \cventry{New Computational Tools for Top-Down and Bottom-Up Natural Product Drug Discovery}{}{}{Nov 2021 }{\begin{cvitems}
\item Computation \& Informatics in Biology \& Medicine Seminars BMI 915
\end{cvitems}}
    \cventry{IDBac: Bioinformatics Software for Microbial Drug Discovery Prioritization and Culturomics Characterization}{}{}{Jun 2020 }{\begin{cvitems}
\item St. Jude National Graduate Student Symposium (cancelled due to Covid19)
\end{cvitems}}
    \cventry{Protein MS isn't the only MS… Programming in R for Metabolomics Mass Spectrometry}{}{}{May 2020 }{\begin{cvitems}
\item May Institute 2020: Future developers meeting
\end{cvitems}}
    \cventry{IDBac: Bioinformatics Software for Microbial Drug Discovery Prioritization and Culturomics Characterization}{}{}{Feb 2020 }{\begin{cvitems}
\item Gordon Research Conference on Marine Natural Products
\item Gordon Research Seminar (GRS) on Marine Natural Products
\end{cvitems}}
    \cventry{Your Missing Step in Reproducible R Programming: Continuous Deployment}{}{}{Aug 2019 }{\begin{cvitems}
\item R/Pharma, Harvard University
\end{cvitems}}
    \cventry{Bioinformatics in R}{}{}{Apr 2019 }{\begin{cvitems}
\item satRdays Chicago
\end{cvitems}}
    \cventry{Single Function Lightning Talks: “lengths(), not length()”}{}{}{Jan 2019 }{\begin{cvitems}
\item Chicago R User Group
\end{cvitems}}
    \cventry{IDBac: A New Paradigm in Developing Microbial Libraries for Drug Discovery}{}{}{Aug 2018 }{\begin{cvitems}
\item R/Pharma, Harvard University
\end{cvitems}}
    \cventry{IDBac: A Shiny App to Analyze Bacterial Fingerprints and Aid in the Discovery of Potential New Antibiotics}{}{}{Jan 2018 }{\begin{cvitems}
\item Chicago R User Group
\end{cvitems}}
    \cventry{IDBac: A proteomic \& chemometric pipeline for rapid bacterial characterization}{}{}{Mar 2017 }{\begin{cvitems}
\item Center for Biomolecular Sciences, UIC
\end{cvitems}}
    \cventry{Rational design of bacterial strain libraries for drug discovery}{}{}{Nov 2016 }{\begin{cvitems}
\item UIC Specialized Metabolite Community
\end{cvitems}}
    \cventry{Use of MALDI-MS to Create `Smart' Libraries for Drug-Lead Discovery}{}{}{Jul 2016 }{\begin{cvitems}
\item Chicago Mass Spec Day
\end{cvitems}}
    \cventry{HPLC-DAD Method for Trace Detection of Benzoic and Sorbic Acids in High Protein Matrices}{}{}{Apr 2015 }{\begin{cvitems}
\item SSAOAC Annual Meeting
\end{cvitems}}
\end{cventries}

\hypertarget{in-progress}{%
\section{In-Progress}\label{in-progress}}

\begin{cventries}
    \cventry{Web resource for sharing and searching FAIR MALDI-MS microbial spectra}{}{}{IDBacDB Manuscript}{}\vspace{-4.0mm}
    \cventry{Repository-scale analyses of protein similarity}{}{}{SocialGene Manuscript}{}\vspace{-4.0mm}
    \cventry{Multinational collaboration to create a standardized collection of NP HMM models}{}{}{clusterrule Manuscript}{}\vspace{-4.0mm}
    \cventry{Code standardization and enhancements including addition of a Nextflow pipleine}{}{}{Autometa 2.0 Manuscript}{}\vspace{-4.0mm}
    \cventry{Co-writing a review on genome resolved metagenomics and natural product discovery}{}{}{Metagenomics Review Manuscript}{}\vspace{-4.0mm}
    \cventry{Mapping transcriptional regulation in Actinobacteria}{}{}{Transcriptomics}{}\vspace{-4.0mm}
    \cventry{Improving multisample genome resolved metagenomics}{}{}{Metagenomics}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{select-individual-software-projects}{%
\section{Select Individual Software
Projects}\label{select-individual-software-projects}}

\begin{cventries}
    \cventry{socialgene}{Python, Django, Nextflow, Rust, High-throughput computing}{Repository-scale genome pattern search platform}{2021-2023}{}\vspace{-4.0mm}
    \cventry{electricShine}{R, Javascript, Node/Electron}{Shiny packaging with Electron}{2019}{}\vspace{-4.0mm}
    \cventry{mzEasy}{R, Shiny}{Shiny app for converting and visualizing mass spectrometry data}{2019}{}\vspace{-4.0mm}
    \cventry{mzPlotter}{R, Rmarkdown}{Automated summary of of LC-MS/MS data with interactive Rmarkdown reports}{2019}{}\vspace{-4.0mm}
    \cventry{mzFromImage}{R, Shiny}{Predict a mass spectrum’s values from a static image file}{2019}{}\vspace{-4.0mm}
    \cventry{mgfparse}{R}{Low-dependency R package for quickly and efficiently parsing mgf files into R}{2019}{}\vspace{-4.0mm}
    \cventry{IDBac}{R, Shiny, Electron}{MALDI protein and small molecule bioinformatics platform}{2018-2023}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{select-team-software-projects}{%
\section{Select Team Software
Projects}\label{select-team-software-projects}}

\begin{cventries}
    \cventry{metaBenchmarks}{Nextflow}{Benchmark metagenomic profiling/binning software}{2021}{}\vspace{-4.0mm}
    \cventry{Autometa}{Python, Nextflow}{Automated binning pipeline for single metagenomes}{2020-2023}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{workshops-host}{%
\section{Workshops (host)}\label{workshops-host}}

\begin{cventries}
    \cventry{ASP Annual Meeting (Co-host)}{}{}{Jul 2022 }{\begin{cvitems}
\item Hands-On training of IDBac, an informatics tool for strain prioritization
\end{cvitems}}
    \cventry{Department of Pharmacognosy}{}{}{May 2019 }{\begin{cvitems}
\item IDBac tutorial
\end{cvitems}}
\end{cventries}

\hypertarget{workshops-participant}{%
\section{Workshops (participant)}\label{workshops-participant}}

\begin{cventries}
    \cventry{Artificial Intelligence for Natural Product Drug Discovery (Invitation-Only; Lorentz Center)}{}{}{Sep 2021 }{}\vspace{-4.0mm}
    \cventry{Integration of Metabolomics and Genomics (University of Chicago)}{}{}{Aug 2019 }{}\vspace{-4.0mm}
    \cventry{PATRIC/RAST Workshop (Argonne National Laboratory)}{}{}{Dec 2016 }{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\hypertarget{invited-guest-lectures}{%
\subsection{Invited Guest Lectures}\label{invited-guest-lectures}}

\begin{cventries}
    \cventry{PSCI 522 Advanced Pharmacognosy (two lectures)}{}{University of Illinois at Chicago}{Spring 2022}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{peer-review}{%
\section{Peer Review}\label{peer-review}}

\begin{itemize}
\item
  Journal of Natural Products
\item
  CRC press
\item
  rOpenSci
\item
  Microbiology Spectrum
\end{itemize}

\hypertarget{membershipsprofessional-affiliations}{%
\section{Memberships/Professional
Affiliations}\label{membershipsprofessional-affiliations}}

\begin{itemize}
\tightlist
\item
  American Society of Pharmacognosy
\item
  Chicago R User Group
\item
  Chicago Python User group
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

The code for building this CV is available at:
\url{https://github.com/chasemc/resume}



\end{document}
