---
name: Nathaniel Price
docname: "Resume"
fontawesome: yes
address: "Denver, Colorado"
phone: "+1 904 315 2486"
email: "natbprice@gmail.com"
www: "natbprice.github.io"
date: "`r format(Sys.time(), '%B %Y')`"
output: function(...) {source('price_entries.R');vitae:::set_entry_formats(price_entries);vitae::cv_document(..., template = "pricetemplate.tex", citation_package = "biblatex")}
---

```{r setup, include=FALSE}
# To save log files
# rmarkdown::render("resume/nprice_resume.Rmd", clean = FALSE)

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

library(tidyverse)
library(vitae)
library(lubridate)
library(glue)
library(rlang)
```

```{r loadData}

# Education
education <- read_csv("../data/education.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")
                        )
                      )

# Job titles
job.titles <- read_csv("../data/job-titles.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")
                        )
)

# Skills
skills <- read_csv("../data/skills.csv")

# Job descriptions
job.descriptions <- read_csv("../data/job-descriptions.csv")

# Awards
awards <- read_csv("../data/awards.csv")

```

# Education
```{r education, results = "asis"}

# Merge joint PhD entries
education %>%
  arrange(desc(end), begin) %>%
  mutate(what = degree,
         when = year(end),
         with = university,
         where = glue("{city}, {region}, {country}")) %>% 
  select(what, when, with, where) %>% 
  group_by(what, when) %>% 
  summarize(what = nth(what, 1),
            when = nth(when, 1),
            with = if_else(n() > 1, glue("{nth(with, 1)} and {nth(with, 2)}"), nth(with, 1)),
            where = if_else(n() > 1, glue("{nth(where, 1)} and {nth(where, 2)}"), nth(with, 1)),
            .groups = "drop") %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what,
    when,
    with,
    where,
    .protect = F
  )

```

# Experience

```{r experience}
job.titles %>% 
  # Only 5 most recent jobs
  arrange(desc(begin)) %>% 
  filter(year(begin) >= 2010) %>%
  # Join job descriptions
  left_join(job.descriptions) %>% 
  # Arrange by descending begin date
  arrange(desc(begin), descId) %>% 
  # Format as detailed entries
  detailed_entries(
    what = position,
    when = as.character(
      glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - 
           {if_else(!is.na(end), 
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'present')}")),
    with = employer,
    where = glue("{city}, {region}, {country}"),
    why = accomplishments)
```

# Data Science Skills

```{r}
skills_formatted <- skills %>% 
  mutate(skill = if_else(is.na(details), glue("{skill}"), glue("{skill} ({details})"))) %>% 
  group_by(group) %>% 
  summarize(skills = glue_collapse(skill, sep = " $\\bullet$ "))
```

```{r, results='asis', width = 40000}
for (group in skills_formatted$group) {
  cat(
    glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"),
    filter(skills_formatted, group == !!group)$skills,
    "\n\n\n"
  )
}
```

# Publications

\faicon{book} `r bibliography_entries("publications.bib") %>% filter(type == "chapter") %>% summarize(N = n()) %>% pull(N)` book chapters

\faicon{file-text} `r bibliography_entries("publications.bib") %>% filter(type == "article-journal") %>% summarize(N = n()) %>% pull(N)` peer-reviewed journal publications

\faicon{pencil} `r bibliography_entries("publications.bib") %>% filter(type == "paper-conference") %>% summarize(N = n()) %>% pull(N)` conference papers

\faicon{floppy-o} `r bibliography_entries("publications.bib") %>% filter(id %in% c("price_radsets_2019", "price_tvdiff_2019", "price_huntfishapp_2019")) %>% summarize(N = n()) %>% pull(N)` open-source software packages

Full List Available on Google Scholar: https://scholar.google.com/citations?hl=en&user=rXaKU0EAAAAJ

## Open Source Software

```{r}
bibliography_entries("publications.bib") %>%
  filter(id %in% c("price_radsets_2019", "price_tvdiff_2019", "price_huntfishapp_2019"))
```


## Select Publications
```{r}
bibliography_entries("publications.bib") %>%
  filter(
    id %in% c(
      "balesdent_advanced_2016",
      "chaudhuri_nasa_2015",
      "price_open-sourced_2020",
      "hinrichs_understanding_2020"
    )
  ) %>%
  arrange(desc(issued))
```

\fancyfoot[LO,LE]{\footnotesize This resume was generated on `r Sys.time()` using vitae R package and custom LaTeX template (\href{https://github.com/natbprice/cv}{github.com/natbprice/cv})}